\thesistitle

### 2019-07-29 sections/clonerefactor.tex
Better total order formulas

\begin{equation}\label{eq:rangetotalorder}
R_1 < R_2 \text{ iff } end\_line(R_1) < begin\_line(R_2) \lor (end\_line(R_1) = begin\_line(R_2) \land end\_column(R_1) < begin\_column(R_2))
\end{equation}
\begin{equation}\label{eq:rangetotalorder2}
R_1 > R_2 \text{ iff } begin\_line(R_1) > end\_line(R_2) \lor (begin\_line(R_1) = end\_line(R_2) \land begin\_column(R_1) > end\_column(R_2))
\end{equation}

>>>>

\begin{equation}\label{eq:rangetotalorder}
r_1 < r_2 \text{ iff } ELr_1 < BLr_2 \lor (ELr_1 = BLr_2) \land ECr_1 < BCr_2)
\end{equation}
\begin{equation}\label{eq:rangetotalorder2}
r_1 > r_2 \text{ iff } BLr_1 > ELr_2 \lor (BLr_1 = ELr_2 \land BCr_1 > ECr_2)
\end{equation}

Where \textit{BL} is the begin line of a range, \textit{EL} is the end line of a range, \textit{BC} is the begin column of a range and \textit{EC} is the end column of a range.
